### 2010-07-23 papers/icfp-2010-desc/paper_desc_levitation.tex
Desc@ICFP: set polymorphism in Coq model

To demystify the apparent circularity of our construction, let us
consider how it bottoms out in a stratified setting. Using the
informal level annotations of Section~\ref{sec:universe-desc}, we have
that \(\Bhab{\DescD^n}{\Desc^{n+1}}\), hence \(\Bhab{\Desc^n \mapsto
  \Mu{\DescD^n}}{\Set^{n+1}}\). Assuming an hardwired $\Desc^N$
universe, we can build the tower of descriptions down to $\Desc^0$:
description of descriptions forms a `spiral', rather than a
circle \footnote{We have modelled this process in Agda, hardwiring
  $\Desc^{42}$ in $\Set^{43}$, then going down. This model does not
  rely on dependent pattern-matching, induction-recursion, nor set
  polymorphism.}. Hence, in a stratified system, the `self-encoded'
nature of $\Desc$ appears only in a set polymorphic sense: the
principal type of the levitating description generalizes to the type
of $\Desc$ itself\footnote{This is witnessed in our set polymorphic
  model in Agda. Set polymorphism is an experimental feature of
  Agda. Although not backed by theoretical works, it is a conservative
  extension of Agda that is generally accepted as free of paradox.}.

>>>>

To demystify the apparent circularity of our construction, let us
consider how it bottoms out in a stratified setting. Using the
informal level annotations of Section~\ref{sec:universe-desc}, we have
that \(\Bhab{\DescD^n}{\Desc^{n+1}}\), hence \(\Bhab{\Desc^n \mapsto
  \Mu{\DescD^n}}{\Set^{n+1}}\). Assuming an hardwired $\Desc^N$
universe, we can build the tower of descriptions down to $\Desc^0$:
description of descriptions forms a `spiral', rather than a
circle \footnote{We have modelled this process in Agda, hardwiring
  $\Desc^{42}$ in $\Set^{43}$, then going down. This model does not
  rely on dependent pattern-matching, induction-recursion, nor set
  polymorphism.}. Hence, in a stratified system, the `self-encoded'
nature of $\Desc$ appears only in a set polymorphic sense: the
principal type of the levitating description generalizes to the type
of $\Desc$ itself\footnote{This is witnessed in our set polymorphic
  model in Agda and in our Coq model, crucially relying on typical
  ambiguity~\cite{harper:implicit-universe}.}.
